---
title: "CSE3506_PROJECT"
author: "KEERTHANA S_20BCE1049"
date: "2022-12-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Predicting Hit Songs**

## Dataset

```{r}
#Loading dataset
data = read.csv("datasets/categ_to_num.csv")
```
```{r}
```
## Normalization

```{r}
data$artist=as.numeric(data$artist)
```
```{r}
#Applying min-max normalization method
min_max_normalisation <- function(x) {
    (x-min(x))/(max(x)-min(x))
    #(x-mean(x))/sd(x)
    #(x-(quantile(x)[2]))/((quantile(x)[4])-(quantile(x)[2]))
}
```
```{r}
data$loudness=round(min_max_normalisation(data$loudness),4)
data$duration_ms=round(min_max_normalisation(data$duration_ms),4)
data$tempo=round(min_max_normalisation(data$tempo),4)
data$chorus_hit=round(min_max_normalisation(data$chorus_hit),4)
```
```{r}
#Converting scientific to numeric values
data$instrumentalness = format(data$instrumentalness,scientific = F)
data$instrumentalness=round(as.double(substring(data$instrumentalness,1,8)),4)

```
```{r}
write.csv(data,"datasets/normalized_data.csv",row.names = F)
```
head(data)
```

## Normalization of data with explicit column

```{r}
#Loading dataset
data_explicit = read.csv("datasets/combined_data_explicit.csv")

```

```{r}
data_explicit$artist=as.numeric(data_explicit$artist)
```
```{r}
#Applying min-max normalization method
min_max_normalisation <- function(x) {
    (x-min(x))/(max(x)-min(x))
    #(x-mean(x))/sd(x)
    #(x-(quantile(x)[2]))/((quantile(x)[4])-(quantile(x)[2]))
}
```
```{r}
data_explicit$loudness=round(min_max_normalisation(data_explicit$loudness),4)
data_explicit$duration_ms=round(min_max_normalisation(data_explicit$duration_ms),4)
data_explicit$tempo=round(min_max_normalisation(data_explicit$tempo),4)
data_explicit$chorus_hit=round(min_max_normalisation(data_explicit$chorus_hit),4)
```
```{r}
#Converting scientific to numeric values
data_explicit$instrumentalness = format(data_explicit$instrumentalness,scientific = F)
data_explicit$instrumentalness=round(as.double(substring(data_explicit$instrumentalness,1,8)),4)

```
```{r}
write.csv(data_explicit,"datasets/normalized_explicit_data.csv",row.names = F)
```


